\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-04-24 doc/paper.tex
Edited abstract for readability.

  \begin{abstract}
   We introduce \fs, a MATHEMATICA package which generates a C++
   spectrum generator for any SUSY model, created with modularity and
   speed in mind.  \fs makes use of the existing \sarah package
   to obtain self energies, tadpole corrections and renormalisation
   group equations in any model.  \fs then generates C++ code for
   calculating spectra with a structure that is designed to be
   flexible. The user specifies the model supplying the
   superpotential, gauge structure and particle content in a \sarah
   model file. The user should also specify the boundary conditions in
   a separate \fs model file.  Flexible SUSY
   then translates these into C++ code along with numerical routines
   for solving the renormalisation group equations, one loop
   electroweak symmetry breaking conditions and a solver routine for
   simultaneously solving for the spectrum.  The modular structure of
   the generated code allows for any individual component to be
   replaced with an alternative if available.  Indeed \fs has been
   intentionally designed to grow as alternative solvers and
   calculators are added.
  \end{abstract}
\begin{keyword}
sparticle, 
supersymmetry, 
Higgs
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}

>>>>

  \begin{abstract}
   We introduce \fs, a MATHEMATICA package which generates a fast,
   precise C++ spectrum generator for any SUSY model specified by the
   user.  The generated code is designed with both speed and
   modularity in mind, making it easy to adapt and extend with new
   features. The user specifies the model supplying the
   superpotential, gauge structure and particle content in a \sarah
   model file and provides specific the boundary conditions in a
   separate \fs model file. \fs makes use of the existing \sarah
   package to obtain self energies, tadpole corrections,
   renormalisation group equations(RGEs) and tree level mass and
   electroweak symmetry breaking conditions for the specified model. These are
   translated into C++ code and combined  with numerical
   routines for solving the RGEs, EWSB conditions and simultaneously
   solving for the spectrum conssistent with user specified boundary
   conditions.  The modular structure of the generated code allows for
   individual components to be replaced with an alternative if
   available. \fs has been carefully designed to grow as
   alternative solvers and calculators are added.
  \end{abstract}

\begin{keyword}
sparticle, 
supersymmetry, 
Higgs
\PACS 12.60.Jv
\PACS 14.80.Ly
\end{keyword}
\end{frontmatter}
